%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Compressed Entries  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\TowerDefence}{
    \poswithprd{Tower Defense Game}{Sept 2016-Oct 2016}
    \begin{minipage}[t]{\miniwidth}
    \begin{itemize}
        \item   
        Designed a robotic car, which could run along the track and stop under conditions specified by the rules.
        \item
        Designed a tower, which used distance sensors to locate the robotic cars and used a LASER to shoot the cars.
        \item 
        Used Arduino to implement the car and the tower.
        \end{itemize}
    \end{minipage}
}

\newcommand{\RoboticsCompetition}{
    \poswithprd{SJTU Freshmen Robotics Competition}{Mar 2017-Apr 2017}
    \begin{minipage}[t]{\miniwidth}
        \begin{itemize}
            \item
            Designed and implemented a robot to catch and transport various objects.
            Won championship.
            \item 
            Worked in a team of eight. Responsible for the design of the frame.
        \end{itemize}
    \end{minipage}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Active Entries  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\NewPart{Projects}

\SJTU
\poswithprd{HackxSJTU}{June 2018}\\
\begin{minipage}[t]{\miniwidth} 
    \begin{itemize}
        \item
        Designed an AR navigation application, which could place pets at crossings to indicate  directions.
        \item
        Used Unity and ARCore to implement the application on Android devices. Used C\# to control the motion of the pets.
    \end{itemize}
\end{minipage}
\vspace{\betweenEntry}

\RoboticsCompetition
\vspace{\betweenEntry}

\JI
\poswithprd{Parking Lots System Design}{July 2017-Aug 2017}\\
\begin{minipage}[t]{\miniwidth}
    \begin{itemize}
        \item 
        Designed a parking lot system to arrange the charge and positions using C++.
        \item 
        Used OpenGL to visualize the parking lot.
    \end{itemize}
\end{minipage}
\vspace{\betweenEntry}

\TowerDefence
